% EP, MT, Hur, KatoF

\begin{thebibliography}{99999999}
\bibitem[KatoF]{KatoF} F.~Kato, \textit{Log smooth deformation and moduli of log smooth curves}, Int. J. Math. \textbf{11} (2000), no. 2, 215–-232.

\bibitem[MT]{MT} S.~Mochizuki and A.~Tamagawa, \textit{The algebraic and anableian geometry of configuration spaces}, Hokkaido Math. J. \textbf{37} (2008), 75--131.

\bibitem[DM]{DM} P.~Deligne and D.~Mumford, \textit{The irreducibility of the space of curves of given genus}, IHES Publ. Math. \textbf{36} (1969), 75--109.

\bibitem[Hur]{Hur} S.~Mochizuki, \textit{The geometry of the compactification of the Hurwitz scheme}, Publ. Res. Inst. Math. Sci. \textbf{31} (1995), 355--441.

\bibitem[CmbGC]{CmbGC} S.~Mochizuki, \textit{A combinatorial version of the Grothendieck conjecture}, Tohoku Math. J. \textbf{59} (2007), 455--479.

\bibitem[CbGT]{CbGT} Y.~Hoshi, A.~Minamide, and S.~Mochizuki, \textit{Group-theoreticity of numerical invariants and distinguished subgroups of configuration space groups}, Kodai Math. J. \textbf{45} (2022), 295--348.

\bibitem[NodNon]{NodNon} Y.~Hoshi and S.~Mochizuki, \textit{On the combinatorial anabelian geometry of nodally nondegenerate outer representations}, Hiroshima Math. J. \textbf{41} (2011), 275--342.

\bibitem[CbTpI]{CbTpI} Y.~Hoshi and S.~Mochizuki, \textit{Topics surrounding the combinatorial anabelian geometry of hyperbolic curves I: Inertia groups and profinite Dehn twists}, Galois-Teichm\"{u}ller Theory and Arithmetic Geometry, Adv. Stud. Pure Math., \textbf{63}, Math. Soc. Japan (2012), 659--811.

\bibitem[Hoshi1]{Hoshi1} Y.~Hoshi, \textit{The exactness of the log homotopy sequence}, Hiroshima Math. J. \textbf{39} (2009), 61--121.

\bibitem[Vidal]{Vidal} I.~Vidal, \textit{Morphismes log \'{e}tales et descents par hom\'{e}omorphismes universels}, C. R. Math. Acad. Sci. Paris. \textbf{332} (2001), 239--244.

\bibitem[Kisin]{Kisin} M.~Kisin, \textit{Prime to $p$ fundamental groups and tame Galois actions}, Annals de l'Institut Fourier \textbf{50}, no. 4 (2000), 1099--1126.

\end{thebibliography}

